Paper Figures

### 2019-08-20 PaperFigures.Rmd
all 6 groups for total cd4 and pma

```{r}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/comp_hc_ltbi.R")

@@

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    scale_x_discrete(labels=c("HC\nSM-", "HC\nSM+", "LTBI\nSM-", "LTBI\nSM+", "TB\nSM-", "TB\nSM+"))+
    theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(
        comparisons = list(c("HC SM+", "HC SM-"),c("LTBI SM+", "LTBI SM-"), c("TB SM+", "TB SM-")),
        label="p.signif", hide.ns = TRUE, size=8,
        label.y = boxplot.stats(data[,yval])$stats[5]*1.4)+
        coord_cartesian(ylim=c(0, boxplot.stats(data[,yval])$stats[5]*1.5))+
        labs(x="", y="")
}

@@

```{r}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
CD4<-read.csv("ICS_CD4_clean.csv")
CYT<-read.csv("ICS_CD4_Cytokine_clean.csv")
PHEN<-read.csv("ICS_CD4_phenotyping_clean_NAs.csv")
OG<-read.csv("OG_CD4_bulk_summary_clean.csv")
OGPHEN<-read.csv("OG_CD4_OG_summary_clean_NAs.csv")
OG.IFNg<-read.csv("OG_CD4_OG.IFNg_summary_clean_NAs.csv")
OG.GT<-read.csv("OG_CD4_OG.GT_summary_clean_NAs.csv")
luminex<-read.csv("/Applications/Old Computer/Day Lab/Luminex/Clean Data/Luminex_combined_background.txt")
```

#All groups
```{r, fig.height=6, fig.width=3}
cd4<-plot_filter(subset(CD4, CD4$Stim=="UN"))
cyt<-plot_filter(subset(CYT, CYT$Stim=="PMA"))
phen<-plot_filter(subset(PHEN, PHEN$Stim=="PMA"))
og<-plot_filter(subset(OG, OG$Stim=="SEB"))
ogphen<-plot_filter(subset(OGPHEN, OGPHEN$Stim=="SEB"))
```

@@

#Healthy Adults
####The frequency of T-bet+ CD4+ T cells is lower amongst SM+ Healthy Adults  
```{r, fig.height=6, fig.width=3}
cd4<-filter_hc(subset(CD4, CD4$Stim=="UN"))
cyt<-filter_hc(subset(CYT, CYT$Stim=="PMA"))
phen<-filter_hc(subset(PHEN, PHEN$Stim=="PMA"))
og<-filter_hc(subset(OG, OG$Stim=="SEB"))
ogphen<-filter_hc(subset(OGPHEN, OGPHEN$Stim=="SEB"))
```

####Generic cytokine production from CD4+ T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.height=6, fig.width=10}
melt<-melt(cyt, id.vars=c("TB","SM"), measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
cyt_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))
baseplot(melt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")
```

@@

*Which of these orientations makes the point better?*

```{r, fig.height=10, fig.width=5}
test<-melt(phen, id.vars=c("TB", "SM"), 
           measure.vars=c("TH1_T-bet", "TH1_GATA3", "TH1_CXCR3", "TH1_CCR4",
           "TH2_T-bet", "TH2_GATA3", "TH2_CXCR3", "TH2_CCR4"))

@@

####LTBI individuals coinfected with S. mansoni have higher Mtb peptide-specific total cytokine production, specifically due to higher co-production of IFNγ and TNFa
```{r, fig.height=6, fig.width=10}
cyt<-filter_ltbi(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))
og<-filter_ltbi(subset(OG, OG$Stim=="PEP"))
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
oggt<-filter_ltbi(subset(OG.GT, OG.GT$Stim=="PEP"))

#generate cytokine table for graphing
melt<-melt(cyt, 
    id.vars=c("TB","SM"), 
    measure.vars=c("Cyt.Freq", "TH1.Freq", "TH1.2.Freq", "TH2.Freq", "G_x_x_T"))
cyt_groups <- as_labeller(c("Cyt.Freq" = "Total", "TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2", "G_x_x_T"="IFNγ\n&\nTNFa"))
#graph with facets
a<-baseplot(melt[melt$variable!="G_x_x_T",], "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")
b<-baseplot(melt[melt$variable=="G_x_x_T",], "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="")
```

a<-baseplot(melt[melt$variable=="T-bet",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    labs(y="(%) Total CD4+ T cells")

b<-baseplot(melt[melt$variable=="GATA3",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)

c<-baseplot(melt[melt$variable=="CXCR3",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)

d<-baseplot(melt[melt$variable=="CCR4",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)

@@

a<-baseplot(melt[melt$variable=="IFNg",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")

b<-baseplot(melt[melt$variable=="TNFa",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

c<-baseplot(melt[melt$variable=="IL4",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

d<-baseplot(melt[melt$variable=="IL13",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

@@

```{r, fig.height=6, fig.width=10}
#generate cytokine table for graphing
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))
cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))
#graph with facets
baseplot(melt, "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")
```

####Mtb-specific TH1 cytokine producing cells express both TH1 and TH2 lineage-specific markers, however this does not differ by S. mansoni status
*which of these formats do you like? It may be better to look at the active TB data first*
```{r, fig.height=6, fig.width=10}
#graph phenotype
melt<-melt(phen, id.vars=c("TB", "SM"), measure.vars = grep("TH1_._._._.", names(phen)))
test<-filter(melt, variable!="TH1_x_x_x_x")
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4+ T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFa. 
```{r, fig.width=10, fig.height=6}
a<-baseplot(og, "SM", "OG_freq", ltbi.cols)+
    labs(y="Proliferating CD4+ T cells (%)")+coord_cartesian(ylim=c(0,5))
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._.", names(ogphen)))
test<-melt[-grep("._._._.", melt$variable),]
test<-filter(test, variable!="x_x_x")
test$variable<-factor(test$variable, levels=c(
"T_G_x" ,       
"T_x_x" ,         
"x_G_x" ,         
"T_G_4" ,
"T_x_4" ,         
"x_G_4" ,         
"x_x_4"          
))

@@

####Furthermore, IFNγ and TNFa are also the two dominant cytokines produced when analyzed by luminex. The concentration of all cytokines measured by luminex are equivalent between SM- and SM+ groups.
```{r, fig.height=10, fig.width=8}
lum<-filter_ltbi(subset(luminex, luminex$Stim=="PEP"))
names(lum)<-gsub("IL", "IL-", names(lum))
names(lum)<-gsub("IFNg", "IFNγ", names(lum))
names(lum)<-gsub("TNFa", "TNFα", names(lum))

melt<-melt(lum, id.vars=c("TB", "SM"), measure.vars=grep("pg", names(lum)))
melt$variable<-gsub("_pg.ml", "", melt$variable)
melt$variable<- factor(melt$variable, levels=c("TNFα", "IFNγ", "IL-21", "IL-4", "IL-5", "IL-13", "IL-17A", "IL-22", "IL-10"))
booleanplot(melt, "SM", "value", ltbi.cols)+facet_wrap(~variable, scales="free")+labs(y="pg/mL")
```

####However the correlation between cytokines differs between groups. Of note, the correlation between IFNγ and TNFa is stronger amongst SM+ individuals than SM- individuals.
```{r}
df<-lum[,3:11]
names(lum)<-gsub("_pg.ml", "", names(lum))
pca1 <- prcomp(df, scale = TRUE)
pcas<-data.frame(pca1$x)
rotations<-data.frame(pca1$rotation)
rotations$cytokine<-row.names(rotations)
melt<-melt(rotations, id.vars="cytokine")

@@

pos <- cor(lum[lum$SM=="SM+",3:11])
order.pos <- pos[order, order]
res1 <- cor.mtest(lum[lum$SM=="SM+",3:11], conf.level = .95)
pvals <- res1$p[order, order]
corrplot(order.pos, method = "circle", insig = "label_sig", tl.col = "black", 
         p.mat = pvals, sig.level = c(.001, .01, .05), pch.cex = 2, pch.col = "white",
         type="upper")

lum_x<-lum[lum$SM=="SM-",]
df_x<-as.matrix(lum_x[,3:11])
row.names(df_x)<-lum_x$Sample
hc_x <- hclust(as.dist(1-cor(df_x)))
x<-plot(hc_x)

@@

*I maybe want to do some analysis about the fact that now higher frequencies of cells express T-bet and/or GATA3 and that there seems to be a preferential expansion of CCR4+ cells but I honestly don't know how to test that*
```{r, fig.height=6, fig.width=10}
#graph phenotype
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._._.", names(ogphen)))
test<-filter(melt, variable!="x_x_x_x")
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

@@

#TB  
####Similar to QFT+, individuals with active TB, co-infected with S. mansoni maintain function Mtb-specific CD4+ T cell cytokine production. There are higher frequencies of TH1/2 cytokine co-producing CD4+ T cells amongst SM+ individuals, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still TH1 cytokine producing cells.
*Again this is where I need an aesthetics opinion*
```{r tb cytokine ics, fig.width=10, fig.height=6}
cyt<-filter_tb(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_tb(subset(PHEN, PHEN$Stim=="PEP"))
og<-filter_tb(subset(OG, OG$Stim=="PEP"))
ogphen<-filter_tb(subset(OGPHEN, OGPHEN$Stim=="PEP"))

@@

####Mtb-specific TH1 cytokine producing cells express both TH1 and TH2 lineage-specific markers. There are numerous phenotypic differences amongst Mtb-specific TH1 cytokine producing cells betweeen SM- and SM+ groups. While T-bet is still the dominant transcription factor expressed in both groups, most differences are due to higher frequencies of GATA3 and CCR4 co-expressing cells.
```{r, fig.width=10, fig.height=6}
#graph phenotype
melt<-melt(phen, id.vars=c("TB", "SM"), measure.vars = grep("TH1_._._._.", names(phen)))
test<-filter(melt, variable!="TH1_x_x_x_x")
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

@@

>>>>

```{r plot functions}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/comp_hc_ltbi.R")

@@

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    scale_x_discrete(labels=c("HC\nSM-", "HC\nSM+", "LTBI\nSM-", "LTBI\nSM+", "TB\nSM-", "TB\nSM+"))+
    theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(
        comparisons = list(c("HC SM+", "HC SM-"),c("LTBI SM+", "LTBI SM-"), c("TB SM+", "TB SM-")),
        label="p.signif", size=8,
        label.y = boxplot.stats(data[,yval])$stats[5]*1.4)+
        coord_cartesian(ylim=c(0, boxplot.stats(data[,yval])$stats[5]*1.5))+
        labs(x="", y="")
}

@@

```{r load data}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
CD4<-read.csv("ICS_CD4_clean.csv")
CYT<-read.csv("ICS_CD4_Cytokine_clean.csv")
PHEN<-read.csv("ICS_CD4_phenotyping_clean_NAs.csv")
OG<-read.csv("OG_CD4_bulk_summary_clean.csv")
OGPHEN<-read.csv("OG_CD4_OG_summary_clean_NAs.csv")
OG.IFNg<-read.csv("OG_CD4_OG.IFNg_summary_clean_NAs.csv")
OG.GT<-read.csv("OG_CD4_OG.GT_summary_clean_NAs.csv")
luminex<-read.csv("/Applications/Old Computer/Day Lab/Luminex/Clean Data/Luminex_combined_background.txt")
```

#All groups
Dont worry I can change this so the ns bars don't show up, especially for the cytokines since I have no idea why that giant NS is there. But for now I'm leaving them so we know.
```{r}
cd4<-plot_filter(subset(CD4, CD4$Stim=="UN"))
cyt<-plot_filter(subset(CYT, CYT$Stim=="PMA"))
phen<-plot_filter(subset(PHEN, PHEN$Stim=="PMA"))
og<-plot_filter(subset(OG, OG$Stim=="SEB"))
ogphen<-plot_filter(subset(OGPHEN, OGPHEN$Stim=="SEB"))
```

@@

#Healthy Adults
*Is this superfluous now?*  
####Generic cytokine production from CD4+ T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.width=18, fig.height=9.5}
melt<-melt(cyt, id.vars=c("TB","SM"), measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
cyt_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))
baseplot(melt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")+coord_cartesian(ylim=c(0,40))
```

@@

```{r, fig.width=5, fig.height=10}
test<-melt(phen, id.vars=c("TB", "SM"), 
           measure.vars=c("TH1_T-bet", "TH1_GATA3", "TH1_CXCR3", "TH1_CCR4",
           "TH2_T-bet", "TH2_GATA3", "TH2_CXCR3", "TH2_CCR4"))

@@

####LTBI individuals coinfected with S. mansoni have higher Mtb peptide-specific cytokine production, specifically due to higher production of IFNγ
```{r, narrow down ltbi data}
cyt<-filter_ltbi(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))
og<-filter_ltbi(subset(OG, OG$Stim=="PEP"))
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
oggt<-filter_ltbi(subset(OG.GT, OG.GT$Stim=="PEP"))
```

```{r cytokine, fig.width=16, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))
cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))

a<-baseplot(melt[melt$variable=="IFNg",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")

b<-baseplot(melt[melt$variable=="TNFa",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

c<-baseplot(melt[melt$variable=="IL4",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

d<-baseplot(melt[melt$variable=="IL13",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

@@

####Mtb-specific TH1 cytokine producing cells express both TH1 and TH2 lineage-specific markers, however this does not differ by S. mansoni status
```{r ics main four markers, fig.width=16, fig.height=8}
melt<-melt(phen, id.vars=c("TB","SM", "disease"), measure.vars=c("ifng_T-bet", "ifng_GATA3", "ifng_CXCR3", "ifng_CCR4"))
melt$variable<-gsub("ifng_", "", melt$variable)

a<-baseplot(melt[melt$variable=="T-bet",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    labs(y="(%) Total CD4+ T cells")

b<-baseplot(melt[melt$variable=="GATA3",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)
c<-baseplot(melt[melt$variable=="CXCR3",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)

d<-baseplot(melt[melt$variable=="CCR4",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)

@@

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4+ T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFα. 
```{r og and cyt, fig.width=16, fig.height=8}
a<-baseplot(og, "SM", "OG_freq", ltbi.cols)+
    labs(y="Proliferating CD4+ T cells (%)")+coord_cartesian(ylim=c(0,5))
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._.", names(ogphen)))
test<-melt[-grep("._._._.", melt$variable),]
test<-filter(test, variable!="x_x_x")
test$variable<-factor(test$variable, levels=c(
"T_G_x" ,       
"T_x_x" ,         
"x_G_x" ,         
"T_G_4" ,
"T_x_4" ,         
"x_G_4" ,         
"x_x_4"          
))

@@

####Furthermore, IFNγ and TNFa are also the two dominant cytokines produced when analyzed by luminex. The concentration of all cytokines measured by luminex are equivalent between SM- and SM+ groups.
```{r luminex, fig.width=12, fig.height=16}
lum<-filter_ltbi(subset(luminex, luminex$Stim=="PEP"))
names(lum)<-gsub("IL", "IL-", names(lum))
names(lum)<-gsub("IFNg", "IFNγ", names(lum))
names(lum)<-gsub("TNFa", "TNFα", names(lum))

melt<-melt(lum, id.vars=c("TB", "SM"), measure.vars=grep("pg", names(lum)))
melt$variable<-gsub("_pg.ml", "", melt$variable)
melt$variable<- factor(melt$variable, levels=c("TNFα", "IFNγ", "IL-21", "IL-17A", "IL-22", "IL-10", "IL-4", "IL-5", "IL-13"))
booleanplot(melt, "SM", "value", ltbi.cols)+facet_wrap(~variable, scales="free")+labs(y="pg/mL")
```

####However the correlation between cytokines differs between groups. Of note, the correlation between IFNγ and TNFa is stronger amongst SM+ individuals than SM- individuals.
```{r cor plots}
df<-lum[,3:11]
names(lum)<-gsub("_pg.ml", "", names(lum))
pca1 <- prcomp(df, scale = TRUE)
pcas<-data.frame(pca1$x)
rotations<-data.frame(pca1$rotation)
rotations$cytokine<-row.names(rotations)
melt<-melt(rotations, id.vars="cytokine")

@@

pos <- cor(lum[lum$SM=="SM+",3:11])
order.pos <- pos[order, order]
res1 <- cor.mtest(lum[lum$SM=="SM+",3:11], conf.level = .95)
pvals <- res1$p[order, order]
corrplot(order.pos, method = "circle", insig = "label_sig", tl.col = "black", 
         p.mat = pvals, sig.level = c(.001, .01, .05), pch.cex = 2, pch.col = "white",
         type="upper")
```

@@

*I maybe want to do some analysis about the fact that now higher frequencies of cells express T-bet and/or GATA3 and that there seems to be a preferential expansion of CCR4+ cells but I honestly don't know how to test that*

```{r og main four markers, fig.width=16, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-baseplot(melt[melt$variable=="T-bet",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    labs(y="(%) Total CD4+ T cells")+coord_cartesian(ylim=c(0,100))

b<-baseplot(melt[melt$variable=="GATA3",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)+coord_cartesian(ylim=c(0,100))

c<-baseplot(melt[melt$variable=="CXCR3",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)+coord_cartesian(ylim=c(0,100))

d<-baseplot(melt[melt$variable=="CCR4",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)+coord_cartesian(ylim=c(0,100))

```{r og phenotype, fig.width=16, fig.height=8}
#graph phenotype
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._._.", names(ogphen)))
test<-filter(melt, variable!="x_x_x_x")
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

@@

#TB  
####Similar to QFT+, individuals with active TB, co-infected with S. mansoni maintain function Mtb-specific CD4+ T cell cytokine production. There are higher frequencies of TH1/2 cytokine co-producing CD4+ T cells amongst SM+ individuals, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still TH1 cytokine producing cells.
*Again this is where I need an aesthetics opinion*
```{r tb cytokine ics, fig.width=16, fig.height=8}
cyt<-filter_tb(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_tb(subset(PHEN, PHEN$Stim=="PEP"))
og<-filter_tb(subset(OG, OG$Stim=="PEP"))
ogphen<-filter_tb(subset(OGPHEN, OGPHEN$Stim=="PEP"))

@@

####Mtb-specific TH1 cytokine producing cells express both TH1 and TH2 lineage-specific markers. There are numerous phenotypic differences amongst Mtb-specific TH1 cytokine producing cells betweeen SM- and SM+ groups. While T-bet is still the dominant transcription factor expressed in both groups, most differences are due to higher frequencies of GATA3 and CCR4 co-expressing cells.

```{r main four markers, fig.width=16, fig.height=8}
melt<-melt(phen, id.vars=c("TB","SM", "disease"), measure.vars=c("TH1_T-bet", "TH1_GATA3", "TH1_CXCR3", "TH1_CCR4"))
melt$variable<-gsub("TH1_", "", melt$variable)

a<-baseplot(melt[melt$variable=="T-bet",], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    labs(y="(%) Total CD4+ T cells")

b<-baseplot(melt[melt$variable=="GATA3",], "SM", "value", tb.cols)+    
    facet_wrap(~variable)

c<-baseplot(melt[melt$variable=="CXCR3",], "SM", "value", tb.cols)+    
    facet_wrap(~variable)

d<-baseplot(melt[melt$variable=="CCR4",], "SM", "value", tb.cols)+    
    facet_wrap(~variable)

```{r, fig.width=16, fig.height=8}
#graph phenotype
melt<-melt(phen, id.vars=c("TB", "SM"), measure.vars = grep("TH1_._._._.", names(phen)))
test<-filter(melt, variable!="TH1_x_x_x_x")
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

@@

#Supplementary

```{r ics phenotyping, fig.width=16, fig.height=8}
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))

melt<-melt(phen, id.vars=c("TB", "SM"), measure.vars = grep("TH1_._._._.", names(phen)))
test<-filter(melt, variable!="TH1_x_x_x_x")
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

```{r}
lum_x<-lum[lum$SM=="SM-",]
df_x<-as.matrix(lum_x[,3:11])
row.names(df_x)<-lum_x$Sample
hc_x <- hclust(as.dist(1-cor(df_x)))
x<-plot(hc_x)
